\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-09 theory.tex
removed l+x = l sentance in preference for the expansion argument

Figure~\ref{fig:Cl_xi} shows theoretical models for the shear power spectrum $P_\gamma(\ell)$ (equation~\ref{eqn:Pkappa}), and the shear correlation function (equation~\ref{eqn:xiGG}) for the different variations on the approximations listed in Table~\ref{tab:Tl_nu}.   The Standard and Spherical models agree at the few percent level above $\ell>20$ and below $\theta< 100$ arcmin.  The two outliers are the Baseline and Extended `Flat' Sky Limber cases (LF and ELF) where the \citet{kitching/etal:2016} `Flat' Sky approximation has been made with
\be
T_\ell^{\rm `Flat'} = \ell^4 / (\ell + 0.5)^4 = 1-{2\over \ell}+{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, . 
\label{eqn:Tlflat}
\ee    
We argue that applying the approximation, that $\ell \pm x \approx \ell$, where $x$ is small, only to the numerator of equation~\ref{eqn:Tl} is inconsistent.  By comparing the expansions of equations~\ref{eqn:Tl} and~\ref{eqn:Tlflat}, we see that the \citet{kitching/etal:2016} `Flat' Sky approximation effectively introduces a new term $2/\ell$ making it more deviant from the full spherical solution in comparison to the standard $T_\ell = 1$ case.    To our knowledge, this form of the flat-sky approximation has not been used in cosmic shear studies to date.

>>>>

Figure~\ref{fig:Cl_xi} shows theoretical models for the shear power spectrum $P_\gamma(\ell)$ (equation~\ref{eqn:Pkappa}), and the shear correlation function (equation~\ref{eqn:xiGG}) for the different variations on the approximations listed in Table~\ref{tab:Tl_nu}.   The Standard and Spherical models agree at the few percent level above $\ell>20$ and below $\theta< 100$ arcmin.  The two outliers are the Baseline and Extended `Flat' Sky Limber cases (LF and ELF) where the \citet{kitching/etal:2016} `Flat' Sky approximation has been made with
\be
T_\ell^{\rm `Flat'} = \ell^4 / (\ell + 0.5)^4 = 1-{2\over \ell}+{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, . 
\label{eqn:Tlflat}
\ee    
By comparing the Taylor expansions of equations~\ref{eqn:Tl} and~\ref{eqn:Tlflat}, we find that the \citet{kitching/etal:2016} `Flat' Sky approximation includes an extra term, $2/\ell$, making it more deviant from the full spherical solution, than the standard $T_\ell = 1$ case.    To our knowledge, this form of the flat-sky approximation has not been used in cosmic shear studies to date.
